---
title: "Model"
author: "Richard G. Gardiner"
date: "5/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(stargazer)
library(lme4)
library(car)
library(modelr)
library(readxl)

theme_set(theme_light())

data <- read_csv("model_data.csv") %>%
  mutate(Elected = factor(Elected),
         Fullstate = factor(Fullstate),
         court_lower = abs(judicial - lower),
         court_upper = abs(judicial - upper),
         Individualistic = ifelse(Moralistic == 0 & Traditionalistic == 0, 1, 0)) %>%
  rename(total_score = total_value)
```

```{r}
elected <- lmer(total_score ~ Elected + Year + (1 | Fullstate),
             data = data)

stargazer(elected, type = "text", report = ('vc*p'))
```

```{r}
ideology <- lmer(total_score ~ Elected + Year + outside + (1 | Fullstate),
             data = data)

stargazer(ideology, type = "text", report = ('vc*p'))
```


```{r}
interaction <- lmer(total_score ~ Elected + Year + outside + Elected * outside + (1 | Fullstate),
             data = data)

stargazer(interaction, type = "text", report = ('vc*p'))
```

```{r}
controls <- lmer(total_score ~ Elected + Year + 
             Individualistic + Traditionalistic + Professionalization + (1 | Fullstate),
             data = data)
stargazer(controls, type = "text", report = ('vc*p'))
```


```{r}
full_int <- lmer(total_score ~ Elected * outside + Year + 
             Individualistic + Traditionalistic + Professionalization + (1 | Fullstate),
             data = data)

stargazer(full_int, type = "text", report = ('vc*p'))
```

```{r}
full_no_int <- lmer(total_score ~ Elected + Year + outside + 
             Individualistic + Traditionalistic + Professionalization + (1 | Fullstate),
             data = data)

stargazer(full_no_int, type = "text", report = ('vc*p'))
```

```{r}
stargazer(ideology, interaction, controls, full_int, full_no_int, type = "text")
```



## Trying series with other ideology term (this is the one in the final model)

```{r}
ideology2 <- lmer(total_score ~ Elected + Year + court_lower + court_upper + (1 | Fullstate),
             data = data)
stargazer(ideology2, type = "text", report = ('vc*p'))
```

```{r}
interaction2 <- lmer(total_score ~ Elected + Year + court_lower + court_upper + Elected * court_lower +
                       Elected * court_upper + (1 | Fullstate),
             data = data)
stargazer(interaction2, type = "text", report = ('vc*p'))
```

```{r}
full_no_int2 <- lmer(total_score ~ Elected + Year + court_lower +  court_upper + 
             Individualistic + Traditionalistic + Professionalization + (1 | Fullstate),
             data = data)

stargazer(full_no_int2, type = "text", report = ('vc*p'))
```


```{r}
full_int2 <- lmer(total_score ~ Elected * court_lower + Year + Elected * court_upper  +
             Individualistic + Traditionalistic + Professionalization + (1 | Fullstate),
             data = data)

stargazer(full_int2, type = "text", report = ('vc*p'))
```


## Final Models:


```{r}
# stargazer(elected, ideology2, interaction2, full_int2, full_no_int2,
#           type = "html", report = ('vc*p'), out = "model results.doc")
```

## Predictions

```{r}
upper <- data %>%
  data_grid(court_upper, .model = full_no_int2) 

upper %>%
  mutate(pred = predict(full_no_int2, newdata = upper, allow.new.levels = TRUE)) %>%
  group_by(court_upper) %>%
  summarise(pred = mean(pred)) %>%
  ungroup() %>%
  ggplot(aes(x = court_upper, y = pred)) +
  geom_line() +
  theme_light() +
  labs(x = "Ideological Distance: Upper Chamber", y = "Predicted Net-Proportional Sentiment")

# ggsave("upper ideology and sentiment.jpeg")
```


```{r}
individual <- data %>%
  data_grid(Individualistic, .model = full_int2)

individual %>%
  mutate(pred = predict(full_int2, newdata = individual, allow.new.levels = TRUE)) %>%
  group_by(Individualistic) %>%
  summarise(pred = mean(pred)) %>%
  ungroup() %>%
  filter(!is.na(Individualistic)) %>%
  ggplot(aes(x = factor(Individualistic), y = pred)) +
  geom_col() +
  labs(x = "", y = "Predicted Net-Proportional Sentiment") +
  scale_x_discrete(labels = c("Moralistic", "Individualistic"))

# ggsave("culture and sentiment.jpeg")
```

```{r}
professional <- data %>%
  data_grid(Professionalization, .model = full_int2)

professional %>%
  mutate(pred = predict(full_int2, newdata = professional, allow.new.levels = TRUE)) %>%
  group_by(Professionalization) %>%
  summarise(pred = mean(pred)) %>%
  ungroup() %>%
  filter(!is.na(Professionalization)) %>%
  ggplot(aes(x = factor(Professionalization), y = pred)) +
  geom_col() +
  labs(x = "Level of Professionalization", y = "Predicted Net-Proportional Sentiment") +
  scale_x_discrete(breaks = c(1, 2, 3, 4, 5), labels = c("Least", "", "", "", "Most"))

# ggsave("professionalization and predicted sentiment.jpeg")
```



## Alternatives


### Trying it with multiple types
```{r}
election_type <- read_csv("election type.csv") %>%
  select(-1)

selection_sys_data <- data %>%
  left_join(election_type, by = "Fullstate") %>%
  mutate(Fullstate = factor(Fullstate),
         selection_system = factor(MoreDefined))
```

```{r}
basic <- lmer(total_score ~ selection_system + Year + (1 | Fullstate), data = selection_sys_data)

stargazer(basic, type = "text", report = ('cv*p'))
```

```{r}
ideology_system <- lmer(total_score ~ selection_system + Year + outside + (1 | Fullstate), data = selection_sys_data)

stargazer(ideology_system, type = "text", report = ('cv*p'))
```

```{r}
interaction_system <- lmer(total_score ~ selection_system * outside + Year + (1 | Fullstate), data = selection_sys_data)

summary(interaction_system)
```

```{r}
full_no_int_system <- lmer(total_score ~ selection_system + Year + outside + court_lower +  court_upper + 
                           Individualistic + Traditionalistic + Professionalization + (1 | Fullstate),
                           data = selection_sys_data)

summary(full_no_int_system)
```


```{r}
full_int_system <- lmer(total_score ~ selection_system * outside + Year + court_lower +  court_upper + 
                           Individualistic + Traditionalistic + Professionalization + (1 | Fullstate),
                           data = selection_sys_data)

summary(full_int_system)
```

```{r}
# stargazer(basic, ideology_system, interaction_system, full_no_int_system,
#           full_int_system, type = "html", out = "selection system models (variation).doc")
```



## Net Change Analysis

```{r}
net_change <- read_csv("net_change.csv")

change_data <- data %>%
  left_join(net_change, by = c("Fullstate", "Year")) 
```


```{r}
elected_change <- lmer(total_score ~ Elected + (1 | Fullstate),
             data = change_data)

stargazer(elected_change, type = "text", report = ('vc*p'))
```

```{r}
ideology_change <- lmer(total_score ~ Elected + outside + (1 | Fullstate),
             data = change_data)

stargazer(ideology_change, type = "text", report = ('vc*p'))
```


```{r}
interaction_change <- lmer(total_score ~ Elected + outside + Elected * outside + (1 | Fullstate),
             data = change_data)

stargazer(interaction_change, type = "text", report = ('vc*p'))
```

```{r}
controls_change <- lmer(total_score ~ Elected + 
             Individualistic + Traditionalistic + Professionalization + (1 | Fullstate),
             data = change_data)
stargazer(controls_change, type = "text", report = ('vc*p'))
```


```{r}
full_int_change <- lmer(total_score ~ Elected * outside +  
             Individualistic + Traditionalistic + Professionalization + (1 | Fullstate),
             data = change_data)

stargazer(full_int_change, type = "text", report = ('vc*p'))
```

```{r}
full_no_int_change <- lmer(total_score ~ Elected + outside + 
             Individualistic + Traditionalistic + Professionalization + (1 | Fullstate),
             data = change_data)

stargazer(full_no_int_change, type = "text", report = ('vc*p'))
```


## Models that break up selection system

### Data prep
```{r}
selection_type <- read_csv("selection system.csv")

selection_type <- selection_type %>%
  distinct()
```

```{r}
data <- data %>%
  left_join(selection_type, by = "Fullstate") %>%
  select(-State)

data <- data %>%
  mutate(MoreDefined = factor(MoreDefined))
```


### Models

Non partisan is only positive and sig
```{r}
elected_refined <- lmer(total_score ~ MoreDefined + Year + (1 | Fullstate),
             data = data)

stargazer(elected_refined, type = "text", report = ('vc*p'))
```

Nonpartisan is again positive and sig
```{r}
ideology_refined <- lmer(total_score ~ MoreDefined + Year + outside + (1 | Fullstate),
             data = data)

stargazer(ideology_refined, type = "text", report = ('vc*p'))
```

Nonpartisan is positive and sig
```{r}
interaction_refined <- lmer(total_score ~ MoreDefined + Year + outside + Elected * outside + (1 | Fullstate),
             data = data)

stargazer(interaction_refined, type = "text", report = ('vc*p'))
```

Only professional is sig
```{r}
controls_refined <- lmer(total_score ~ MoreDefined + Year + 
             Individualistic + Traditionalistic + Professionalization + (1 | Fullstate),
             data = data)
stargazer(controls_refined, type = "text", report = ('vc*p'))
```

Only professionalization
```{r}
full_int_refined <- lmer(total_score ~ MoreDefined * outside + Year + 
             Individualistic + Traditionalistic + Professionalization + (1 | Fullstate),
             data = data)

stargazer(full_int_refined, type = "text", report = ('vc*p'))
```


only professionalization
```{r}
full_no_int_refined <- lmer(total_score ~ MoreDefined + Year + outside + 
             Individualistic + Traditionalistic + Professionalization + (1 | Fullstate),
             data = data)

stargazer(full_no_int_refined, type = "text", report = ('vc*p'))
```


```{r}
stargazer(interaction_refined, controls_refined, full_int_refined, full_no_int_refined, type = "text")
```


### Diagnostics


I think this is a good graph to include in the results.
```{r}
data %>%
  group_by(MoreDefined) %>%
  mutate(mean_score = mean(total_score),
         sd = sd(total_score),
         lower_bound = (mean_score - sd),
         upper_bound = (mean_score + sd)) %>%
  ungroup() %>%
  ggplot(aes(x = total_score, y = Fullstate, color = MoreDefined)) +
  geom_point() +
  geom_vline(aes(xintercept = mean_score)) +
  geom_vline(aes(xintercept = lower_bound), color = "red", lty = 2) +
  geom_vline(aes(xintercept = upper_bound), color = "red", lty = 2) +
  facet_wrap(~MoreDefined, scales = "free_y", ncol = 1) +
  theme_minimal() +
  labs(x = "Net Sentiment", y = "", color = "Selection System",
       caption = "Black line: Selection Mean \n Red Lines: 1 Standard Deviation")

ggsave("diagnostics.jpeg")
```




## Post Steigerwalt Meeting:

Take out the lmer, add in fixed effects, take out year.

```{r}
elected_new <- lm(total_score ~ Elected + Year +  Fullstate,
             data = data)
# stargazer(elected_new, type = "text", report = ('vc*p'))
```


```{r}
ideology_new <- lm(total_score ~ Elected + Year + outside + Fullstate,
             data = data)

# stargazer(ideology_new, type = "text", report = ('vc*p'))
```


```{r}
interaction_new <- lm(total_score ~ Elected + Year + outside + Elected * outside + Fullstate,
             data = data)

# stargazer(interaction_new, type = "text", report = ('vc*p'))
```

```{r}
controls_new <- lm(total_score ~ Elected + Year + 
             Individualistic + Traditionalistic + Professionalization + Fullstate,
             data = data)
# stargazer(controls_new, type = "text", report = ('vc*p'))
```


```{r}
full_int_new <- lm(total_score ~ Elected * outside + Year + 
             Individualistic + Traditionalistic + Professionalization + Fullstate,
             data = data)

# stargazer(full_int_new, type = "text", report = ('vc*p'))
```

```{r}
full_no_int_new <- lm(total_score ~ Elected + Year + outside + 
             Individualistic + Traditionalistic + Professionalization + Fullstate,
             data = data)

# stargazer(full_no_int_new, type = "text", report = ('vc*p'))
```

```{r}
stargazer(elected_new, ideology_new, interaction_new, controls_new, 
          full_int_new, full_no_int_new, type = "text", report = ('vc*p'))

# stargazer(elected_new, ideology_new, interaction_new, controls_new, 
#           full_int_new, full_no_int_new, type = "html", report = ('vc*p'), out = "main model outputs")
```


```{r}
data %>%
  data_grid(Elected, .model = elected_new) %>%
  add_predictions(elected_new) %>%
  group_by(Elected) %>%
  summarise(mean_pred = mean(pred)) %>%
  ungroup() %>%
  ggplot(aes(x = Elected, y = mean_pred)) +
  geom_col() +
  labs(x = "Selection System", y = "Mean Predicted Net Sentiment",
       caption = "Using Elected Model") +
  geom_hline(yintercept = 0, lty = 2, color = "red")

# ggsave("elected model prediction.jpeg")
```

```{r}
data %>%
  data_grid(Professionalization, .model = full_int_new) %>%
  filter(Fullstate != "Kansas") %>%
  add_predictions(full_int_new) %>%
  group_by(Professionalization) %>%
  summarise(mean_pred = mean(pred)) %>%
  ungroup() %>%
  ggplot(aes(x = factor(Professionalization), y = mean_pred)) +
  geom_col() +
  scale_x_discrete(labels = c("Least", "", "", "", "Most")) +
  labs(x = "Level of Professionalization", y = "Mean Predicted Net Sentiment",
       caption = "Using the Full Model") +
  geom_hline(yintercept = 0, lty = 2, color = "red")

# ggsave("full model predcition professionalization.jpeg")
```


```{r}
data %>%
  data_grid(Traditionalistic, .model = full_int_new) %>%
  filter(Fullstate != "Kansas") %>%
  add_predictions(full_int_new) %>%
  group_by(Traditionalistic) %>%
  summarise(mean_pred = mean(pred)) %>%
  ungroup() %>%
  filter(!is.na(Traditionalistic)) %>%
  ggplot(aes(x = factor(Traditionalistic), y = mean_pred)) +
  geom_col() +
  scale_x_discrete(labels = c("Moralistic", "Traditionalistic")) +
  labs(x = "", y = "Mean Predicted Net Sentiment",
       caption = "Using the Full Model") +
  geom_hline(yintercept = 0, lty = 2, color = "red")

# ggsave("full model prediction traditionalistic.jpeg")
```




#### Curbing Models

```{r}
curbing <- read_csv("curbing_model_data.csv")

abbreviation <- read_csv("selection system.csv") %>%
  distinct(Fullstate, State, MoreDefined)

legislative_control <- read_excel("Legislative Control.xlsx")

political_culture <- read_csv("political culture.csv")

professionalization <- read_csv("ncsl professionalization.csv")
  
outside_ideology <- data %>%
  select(Fullstate, Year, outside)

curbing_data <- curbing %>%
  left_join(abbreviation, by = "State") %>%
  select(-X1) %>%
  left_join(legislative_control, 
            by = c("Fullstate" = "State", "Year")) %>%
  left_join(political_culture, by = c("Fullstate" = "State")) %>%
  left_join(professionalization, by = c("Fullstate" = "State")) %>%
  left_join(outside_ideology, by = c("Fullstate", "Year")) %>%
  mutate(Elected = ifelse(MoreDefined == "Appointment", 0, 1),
         Individualistic = ifelse(Moralistic == 0 & Traditionalistic == 0, 1, 0))

```


```{r}
curbing_data %>%
  summarise(sd = sd(total_sentiment))

data %>%
  summarise(sd = sd(total_score))
```



```{r}
curbing_data %>%
  group_by(Year) %>%
  summarise(total_sentiment = mean(total_sentiment)) %>%
  ggplot(aes(x = Year, y = total_sentiment)) +
  geom_line() +
  expand_limits(y = 0) +
  scale_x_continuous(breaks = seq(2008, 2017, 1)) +
  labs(y = "Net Sentiment")

ggsave("overall sentiment - curbs.jpeg")
```


```{r}
curbing_data %>%
  group_by(Year, Elected) %>%
  summarise(total_sentiment = mean(total_sentiment)) %>%
  ggplot(aes(x = Year, y = total_sentiment, color = factor(Elected))) +
  geom_line() +
  expand_limits(y = 0) +
  scale_x_continuous(breaks = seq(2008, 2017, 1)) +
  labs(y = "Net Sentiment", color = "Selection System") +
  scale_color_discrete(labels = c("Appointed", "Elected"))

ggsave("overall sentiment by selection - curbs.jpeg")
```



```{r}
curbing_elected_new <- lm(total_sentiment ~ Elected + Year +  Fullstate,
             data = curbing_data)
# stargazer(curbing_elected_new, type = "text", report = ('vc*p'))
```


```{r}
curbing_ideology_new <- lm(total_sentiment ~ Elected + Year + outside + Fullstate,
             data = curbing_data)

# stargazer(curbing_ideology_new, type = "text", report = ('vc*p'))
```


```{r}
curbing_interaction_new <- lm(total_sentiment ~ Elected + Year + outside + Elected * outside + Fullstate,
             data = curbing_data)

# stargazer(curbing_interaction_new, type = "text", report = ('vc*p'))
```

```{r}
curbing_controls_new <- lm(total_sentiment ~ Elected + Year + 
             Individualistic + Traditionalistic + Professionalization + Fullstate,
             data = curbing_data)
# stargazer(curbing_controls_new, type = "text", report = ('vc*p'))
```


```{r}
curbing_full_int_new <- lm(total_sentiment ~ Elected * outside + Year + 
             Individualistic + Traditionalistic + Professionalization + Fullstate,
             data = curbing_data)

# stargazer(curbing_full_int_new, type = "text", report = ('vc*p'))
```

```{r}
curbing_full_no_int_new <- lm(total_sentiment ~ Elected + Year + outside + 
             Individualistic + Traditionalistic + Professionalization + Fullstate,
             data = curbing_data)

# stargazer(curbing_full_no_int_new, type = "text", report = ('vc*p'))
```

```{r}
stargazer(curbing_elected_new, curbing_ideology_new, curbing_interaction_new, curbing_controls_new, 
          curbing_full_int_new, curbing_full_no_int_new, type = "text", report = ('vc*p'))

# stargazer(curbing_elected_new, curbing_ideology_new, curbing_interaction_new, curbing_controls_new,
#           curbing_full_int_new, curbing_full_no_int_new, type = "html", report = ('vc*p'), out = "curbing models.doc")
```




```{r}
curbing_data %>%
  data_grid(Elected, .model = curbing_elected_new) %>%
  add_predictions(curbing_elected_new) %>%
  group_by(Elected) %>%
  summarise(mean_pred = mean(pred)) %>%
  ungroup() %>%
  ggplot(aes(x = Elected, y = mean_pred)) +
  geom_col() +
  labs(x = "Selection System", y = "Mean Predicted Net Sentiment",
       caption = "Using Elected Model - Court Curbing") +
  geom_hline(yintercept = 0, lty = 2, color = "red")

ggsave("elected model prediction - curbs.jpeg")
```

```{r}
curbing_data %>%
  data_grid(Professionalization, .model = curbing_full_int_new) %>%
  filter(Fullstate != "Kansas") %>%
  add_predictions(curbing_full_int_new) %>%
  group_by(Professionalization) %>%
  summarise(mean_pred = mean(pred)) %>%
  ungroup() %>%
  ggplot(aes(x = factor(Professionalization), y = mean_pred)) +
  geom_col() +
  scale_x_discrete(labels = c("Least", "", "", "", "Most")) +
  scale_y_continuous(breaks = seq(-3, 7, 1), limits = c(-3, 7)) +
  labs(x = "Level of Professionalization", y = "Mean Predicted Net Sentiment",
       caption = "Using the Full Model - Court Curbing") +
  geom_hline(yintercept = 0, lty = 2, color = "red")

ggsave("full model predcition professionalization - curbs.jpeg")
```


```{r}
curbing_data %>%
  data_grid(Traditionalistic, .model = curbing_full_int_new) %>%
  filter(Fullstate != "Kansas") %>%
  add_predictions(curbing_full_int_new) %>%
  group_by(Traditionalistic) %>%
  summarise(mean_pred = mean(pred)) %>%
  ungroup() %>%
  filter(!is.na(Traditionalistic)) %>%
  ggplot(aes(x = factor(Traditionalistic), y = mean_pred)) +
  geom_col() +
  scale_x_discrete(labels = c("Moralistic", "Traditionalistic")) +
  labs(x = "", y = "Mean Predicted Net Sentiment",
       caption = "Using the Full Model - Court Curbing") +
  geom_hline(yintercept = 0, lty = 2, color = "red")

ggsave("full model prediction traditionalistic - curbs.jpeg")
```





